---
title: "explore_filtering_options"
author: "Sarah Salois"
date: "10/17/2022"
output: html_document
---

## First approach 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE )
library(raster)
library(rasterKernelEstimates)
library(ncdf4)
library(raster)
library(wesanderson)
library(ggplot2)
library(stars)
library(RColorBrewer)
library(terra)
```

## Kernel Based Estimates on in-Memory Raster Images
Example weighted matrix using function focalWeight - which calculates 
a focal ("moving window") weight matrix for use in the focal function. 
The sum of the values adds up to one.


Note - the focal function from package {raster}	calculates focal (moving window)
values for the neighborhood of focal cells using a matrix of weights 
(perhaps in combination w/a function)

```{r}
set.seed(100)
n <- 200
# create a raster object of two populations
r <- raster::raster(
  cbind(matrix(rnorm(n^2),n,n), matrix(rnorm(n^2,2,2),n,n)))
# create a weight matrix
W <- raster::focalWeight(r,c(1,0.04),type='Gauss')
gf <- focalWeight(r, 2, "Gauss")
W3 <- raster::focalWeight(r,c(2,0.04),type='Gauss')
W5 <- raster::focalWeight(r,c(3,0.04),type='Gauss')
W7 <- raster::focalWeight(r,c(2,0.03),type='Gauss')
W7.1 <- raster::focalWeight(r,c(1,0.09),type='Gauss')
W9 <- raster::focalWeight(r,c(2),type='Gauss')

W <- raster::focalWeight(r,c(1,2),type='Gauss')
# calculate the weighted local mean and variance
run.time <- proc.time()
rLocalKDE1 <- rasterLocalMoments(r,W)
print(proc.time() - run.time)
##    user  system elapsed 
##   0.343   0.002   0.102
# plot original image
plot(r)
# plot the weighted mean
plot(rLocalKDE1$mu)
# plot the weighted variance
plot(rLocalKDE1$var)

```

## Frontal data 

Pulling out the lines that call in the netcdf - they work in a regular
script but not here in markdown - odd.
```{r}
# Pull in netcdf
setwd(here::here('nc_files/dd/'))
nc <- nc_open('DD_20180402_20180408-AT-R2018-NESGRID-NWA_SUBSET-PXY_1_1413572-GRAD_SST-BOA-D3_DAT.nc')
nc2 <- nc_open('DD_20170701_20170731-AT-R2018-NESGRID-GRAD_SST-BOA-STACKED.nc')

```


```{r}

# Extract lat, lon, grad, x, y
lon <- ncvar_get(nc, "longitude")
lat <- ncvar_get(nc, "latitude", verbose = F)
grad <- ncvar_get(nc, attributes(nc$var)$names[2])
x <- ncvar_get(nc, attributes(nc$var)$names[3])
y <- ncvar_get(nc, attributes(nc$var)$names[4])
# these are old files so need to replace fillvalue with NA - Kim has updated
# the newer files with _Fillvalue so that R can recognize it and does this 
# utomatically 
fillvalue <- ncatt_get(nc, 'GRAD_SST', "_fillvalue")
grad[grad == fillvalue$value] <- NA
x[x == fillvalue$value] <- NA
y[y == fillvalue$value] <- NA
# close the netcdf
nc_close(nc) 
# save two versions of grad_mag with and w/out frontal threshold (sims here, front below)
sims <- grad
# Just looking at day 4 of this week for now
gradsst5 <- (sims[,,5])
gradsst5 <- t(gradsst5) # needs to be transposed 
# create a raster 
r = raster(gradsst5, xmn = min(lon), xmx = max(lon), 
           ymn = min(lat), ymx = max(lat),
           crs = CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs+ towgs84=0,0,0"))
r = flip(r,2)  # flip it so it is correct orientation
plot(r) # see it! 

# Another way to plot this via ggplot
# Raster into dataframe
gradsst_spdf <- as(r, "SpatialPixelsDataFrame")
gradsst_df <- as.data.frame(gradsst_spdf)
colnames(gradsst_df) <- c("value", "x", "y")
# Set color palette
divpal = rev(brewer.pal(10,'RdYlBu'))
wes_pal <- wes_palette("Zissou1", 20, type = "continuous")
#show_col(pal)
#' Fancy colors
spec_pal <- hcl.colors(25, "spectral", rev = TRUE)
# Plot
ggplot() + # sst
  geom_tile(data = gradsst_df, aes(x=x, y=y, fill = value)) +
  scale_fill_gradientn(colours = wes_pal) +
  theme_bw()
ggplot() + # sst
  geom_tile(data = gradsst_df, aes(x=x, y=y, fill = value)) +
  scale_fill_gradientn(colours = spec_pal) +
  theme_bw()
# Plot with stars package - 
s <- st_as_stars(r)

#print(s)

plot(s, col = spec_pal, main = 'stars')



```


## Gradients after frontal threshold has been applied

**Note: this original was computed before changing the threshold. We determined
that 0.4 was too high in our region (see test_frontal_thresholds.R, 
plot_thresholds.R, plot_resolution_and_thresholds.R, and results folder).


```{r}

# Create frontal array (via setting setting all values < threshold to 0)
front <- grad
threshold = 0.15 # threshold for classifying front old was (0.4)
front[front < threshold] <- 0 # set all values < thresh == 0 
front5 <- (front[,,5])
front5 <- t(front5)

rf5 = raster(front5, xmn = min(lon), xmx = max(lon), 
           ymn = min(lat), ymx = max(lat),
           crs = CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs+ towgs84=0,0,0"))
rf5 = flip(rf5,2)  
plot(rf5, col = spec_pal)
plot(rf5, col = divpal)

```


## Now apply the smoothing function
This uses the weight matrix from first raster 
```{r}
library(patchwork)
# Day 5
# create a weight matrix
# r here is grad_mag, rf5 is the front (after threshold)
W <- raster::focalWeight(rf5,c(1,0.04),type='Gauss')
# calculate the weighted local mean and variance
rLocalKDE2 <- rasterLocalMoments(rf5,W)
# png(filename = 'raster_fronts_day4.png',width = 480, height = 480)
# plot(rf4)
# dev.off()
# plot original image
plot(rf5, main = 'Original', col = spec_pal)
# plot the weighted mean
plot(rLocalKDE2$mu, main = 'Mu', col = spec_pal)
# plot the weighted variance
plot(rLocalKDE2$var, main = 'Var', col = spec_pal)
# Day 4
# run.time <- proc.time()
# rLocalKDE2 <- rasterLocalMoments(rf4,W)
# print(proc.time() - run.time)
# # plot original image
# plot(rf4, main = 'Original')
# # plot the weighted mean
# plot(rLocalKDE2$mu, main = 'Mu')
# # plot the weighted variance
# plot(rLocalKDE2$var, main = 'Var')

```

Do I want to look for neighbors on gradient_sst or frontal_sst maps? 
lets try both. 
```{r}
# W <- raster::focalWeight(rf4,2,type='Gauss')
# create a weight matrix
W1 <- raster::focalWeight(rf5,c(1,0.04),type='Gauss')
W2 <- raster::focalWeight(r,c(1,0.04),type='Gauss')
# calculate the weighted local mean and variance
rLocalKDEfvalid <- rasterLocalMoments(rf5,W1)
rLocalKDEgradmag.org <- rasterLocalMoments(r,W2)
plot(rf5, main = 'Original Fvalid')
p1 = plot(rLocalKDEfvalid$mu, main = 'Mu') # fvalid
plot(r, main = 'Original grad_mag')
p2 = plot(rLocalKDEgradmag.org$mu, main = 'Mu') # gradient_mag
p1 + p2

## compare frontal threshold applied after gaussian filter on grad_sst
# threshold = 0.4 # threshold for classifying front
rLocalKDEgradmag <- rasterLocalMoments(r,W2)
locs <- which(rLocalKDEgradmag$mu@data@values < threshold) 
# set all values < thresh == 0 
rLocalKDEgradmag$mu@data@values[rLocalKDEgradmag$mu@data@values < threshold] <- 0 
locs2 <- which(rLocalKDEgradmag$mu@data@values > threshold) 
rLocalKDEgradmag$mu@data@values[98139]
# alternative way
rLocalKDEgradmag$mu@data@values[locs] <- 0 
p1 = plot(rLocalKDEfvalid$mu, main = 'Mu') # fvalid
p2 = plot(rLocalKDEgradmag.org$mu, main = 'Mu, just grad_mag no filter') # gradient_mag
p3 = plot(rLocalKDEgradmag$mu, main = 'Mu, threshold applied after filter') 
p2 + p3

```

Results suggest that running the local KDE filter on grad_mag then applying
frontal threshold actually reduces the amount of valid frontal pixels 
in th neighborhood and that the correct approach is to run the filter on the fvalid data - after the threshold has been applied. 


***
Some resources on focal statistics: 

[General focal statistics explanation](https://pro.arcgis.com/en/pro-app/latest/tool-reference/spatial-analyst/how-focal-statistics-works.htm#ESRI_SECTION1_CCE941CAD2A4457C8DC706757A832D07)
[Terra focal](https://arc2r.github.io/book/Neighborhood.html)

Second attempt per Chris Haak's suggestion of using focal mean instead of 
threshold would mean just running the first step from above and not using any
threshold after

```{r}
plot(r, col=spec_pal, main = 'Just grad_mag')
rLocalKDEgradmag.org <- rasterLocalMoments(r,W2)
plot(rLocalKDEgradmag.org$mu, main = 'Mu', col=spec_pal) # gradient_mag

```

With raster: 

```{r}
#focal(grad[[1]],fun=mean,w=m)

grad <- t(grad)
b = brick(grad)
b = flip(t(b),2)
f1 <- raster::focal(b[[5]], w = matrix(1, nrow = 3, ncol = 3), fun = sum)
plot(f1, main = "Raster after applying the focal function:raster package",
     cex.main = 1, col = spec_pal)

```

With Terra: 

```{r}
r_spat <- as(r, "SpatRaster")
f2 <- terra::focal(r_spat, w = 3, fun = "sum")
plot(f2, main = "Raster after applying the focal function - terra package", cex.main = 1)

```


## Metrics: 

**Front gradient density:** gdens <- add a gaussian smoothing filter 
(sigma = 5 pixels) to a map of the mean gradient magnitude values 
**Front persistence:** pfront <- the fraction of cloud-free observations of 
a pixel for which a front is detected w/a gaussian filter (sigma = 5 pixels) 
was applied to provide a local neighbourhood average of frontal persistence. 
This is fmean * fprob + weighting factor



```{r}
# Front gradient density: gdens - smoother to mean gradient mag values 
# fmean = sum of gradient values/total number of frontal pixels 
# fvalid
fvalid <- apply(front[,,5], c(1,2), function(x) sum((x > 0)))
# x
x_based_on_mag <- ifelse(front[,,5] > 0.0, x[,,5], NA) # selects values of x only if pixel indicated as frontal from grad_mag
x_sum <- apply(x_based_on_mag, c(1,2),  function(x) sum(na.omit(x)))
# x_var <- apply(x_based_on_mag, c(1,2), function(x) {
#    sum((x - mean(x))^2)/(length(x)-1)})

# y
y_based_on_mag <- ifelse(front[,,5] > 0.0, y[,,5], NA)
y_sum <- apply(y_based_on_mag, c(1,2),  function(x) sum(na.omit(x))) # added na.omit to make it only on frontal pixels


fmean <- (sqrt((x_sum/fvalid)^2 + (y_sum/fvalid)^2))
fmean <- t(fmean)

fmean = raster(fmean, xmn = min(lon), xmx = max(lon), 
           ymn = min(lat), ymx = max(lat),
           crs = CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs+ towgs84=0,0,0"))
fmean = flip(fmean,2)  
plot(fmean)
# create a weight matrix
W <- raster::focalWeight(fmean,c(1,0.04),type='Gauss')
image(W)
W.0 <- raster::focalWeight(fmean,2,type='Gauss')
image(fmean)
image(W.0)
gdens <- rasterLocalMoments(fmean,W)
gdens.0 <- rasterLocalMoments(fmean,W.0)
plot(fmean)
plot(gdens$mu)
plot(gdens.0$mu)

```


In the example where we dont have fronts defined ....

```{r}
weighted_grad <- rLocalKDEgradmag.org$mu





```






```{r}
# Front persistence: pfront <- fraction of cloud-free observations of a pixel 
# for which a front is detected w/a gaussian filter - ie: a local neighbourhood  average of frontal persistence 

fclear_m <- apply(sims[,,5], c(1,2),  function(x) sum(na.omit(x > 0)))

# fprob = front pixels/clear pixels 
fprob = fvalid/fclear_m

fprob <- t(fprob)

fprob = raster(fprob, xmn = min(lon), xmx = max(lon), 
           ymn = min(lat), ymx = max(lat),
           crs = CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs+ towgs84=0,0,0"))

fprob = raster::flip(fprob,2)  
plot(fprob)
# create a weight matrix
W <- raster::focalWeight(fprob,c(1,0.04),type='Gauss')
pfront <- rasterLocalMoments(fprob,W)
plot(fprob)
plot(pfront$mu)



```



## Raster smooth
This code uses function raster.gaussian.smooth from {spatialEco} package. 
Here, sigma is the standard deviation of the kernel and n is the size of 
the focal matrix - this is a simple wrapper for the focal function, which 
returns local statistical moments 

```{r}
library(spatialEco)

# raster is grad_sst of day 5 -- r

kern.r = raster.gaussian.smooth(r, sigma = 2, n = 7, type = mean)
kern.rf5 = raster.gaussian.smooth(rf5, sigma = 2, n = 5, type = mean)
```



```{r}
# Just testing the difference between increasing the weight matrix size
kern.r5 = raster.gaussian.smooth(r, sigma = 2, n = 5, type = mean)
kern.r7 = raster.gaussian.smooth(r, sigma = 2, n = 7, type = mean)

#plot(r, main="original image") 
par(mfrow=c(1,3)) 
plot(r, main="Original") 
plot(kern.r5, main="Sigma = 2, n = 5") 
plot(kern.r7, main="Sigma = 2, n = 7") 

```




```{r}
par(mfrow=c(1,2)) 

plot(rf5, main="original image") 

plot(kern.rf5, main="Gaussian smoothing sigma = 2") 
```


Just testing some stuff 
```{r}


par(mfrow=c(1,3)) 
plot(rf5, main="original frontal image") 

plot(rLocalKDE2$mu, main="using focal weight that is not gaussian") 

plot(kern.rf5, main="Gaussian smoothing sigma = 2") 

```



### Computing the weekly metric w/weighting filter

**Front persistence:** pfront <- the fraction of cloud-free observations of 
a pixel for which a front is detected w/a gaussian filter (sigma = 5 pixels) 
was applied to provide a local neighbourhood average of frontal persistence 

Compute the mean across each raster layer for a given number of days 
Calculate and weight frontal pixels in neighborhood for each image (day) average 
across entire week to get F prox, which summarises the evidence that 
any particular location is in close proximity to a persistent feature. 

```{r}
# Todo: make a function that does this rather than manually : 

# compute front each layer (extract the day, transpose the array)
front1 <- (front[,,1])
front1 <- t(front1)
front2 <- (front[,,2])
front2 <- t(front2)
front3 <- (front[,,3])
front3 <- t(front3)
front4 <- (front[,,4])
front4 <- t(front4)
front5 <- (front[,,5])
front5 <- t(front5)
front6 <- (front[,,6])
front6 <- t(front6)
front7 <- (front[,,7])
front7 <- t(front7)

# create a raster, set the min, max, crs 
rf1 = raster(front1, xmn = min(lon), xmx = max(lon), 
             ymn = min(lat), ymx = max(lat),
             crs = CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs+ towgs84=0,0,0"))

rf1 = flip(rf1,2) # sets accurate orientation

rf2 = raster(front2, xmn = min(lon), xmx = max(lon), 
             ymn = min(lat), ymx = max(lat),
             crs = CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs+ towgs84=0,0,0"))
rf2 = flip(rf2,2) 

rf3 = raster(front3, xmn = min(lon), xmx = max(lon), 
             ymn = min(lat), ymx = max(lat),
             crs = CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs+ towgs84=0,0,0"))
rf3 = flip(rf3,2) 

rf4 = raster(front4, xmn = min(lon), xmx = max(lon), 
             ymn = min(lat), ymx = max(lat),
             crs = CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs+ towgs84=0,0,0"))
rf4 = flip(rf4,2) 



rf5 = raster(front5, xmn = min(lon), xmx = max(lon), 
             ymn = min(lat), ymx = max(lat),
             crs = CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs+ towgs84=0,0,0"))
rf5 = flip(rf5,2) 

rf6 = raster(front6, xmn = min(lon), xmx = max(lon), 
             ymn = min(lat), ymx = max(lat),
             crs = CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs+ towgs84=0,0,0"))
rf6 = flip(rf6,2) 

rf7 = raster(front7, xmn = min(lon), xmx = max(lon), 
             ymn = min(lat), ymx = max(lat),
             crs = CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs+ towgs84=0,0,0"))
rf7 = flip(rf7,2) 

# apply gaussian filter 
kern.rf1 = raster.gaussian.smooth(rf1, sigma = 2, n = 7, type = mean)
kern.rf2 = raster.gaussian.smooth(rf2, sigma = 2, n = 7, type = mean)
kern.rf3 = raster.gaussian.smooth(rf3, sigma = 2, n = 7, type = mean)
kern.rf4 = raster.gaussian.smooth(rf4, sigma = 2, n = 7, type = mean)
kern.rf5 = raster.gaussian.smooth(rf5, sigma = 2, n = 7, type = mean)
kern.rf6 = raster.gaussian.smooth(rf6, sigma = 2, n = 7, type = mean)
kern.rf7 = raster.gaussian.smooth(rf7, sigma = 2, n = 7, type = mean)

# plot(kern.rf3, main="Gaussian smoothing sigma = 2") 
# plot(kern.rf4, main="Gaussian smoothing sigma = 2") 
# plot(kern.rf5, main="Gaussian smoothing sigma = 2") 
# 
# stack and take mean of filter 

f_stack <- stack(kern.rf1, kern.rf2, kern.rf3, kern.rf4,
                 kern.rf5,kern.rf6, kern.rf7)

mean_kern = stackApply(f_stack, c(1,1,1,1,1,1,1), fun = mean)
```



### Visualize

Plots below visualize independent days of the week (after kernel is applied)
and the last image is the averaging of each weighted image across the week 

```{r}
# compare
par(mfrow = c(2,2))
plot(kern.rf3, main= "Day 3") 
plot(kern.rf4, main= "Day 4") 
plot(kern.rf5, main= "Day 5") 
plot(mean_kern, main = 'Fronts w/smoother')
```


### Visualize weekly metric with and w/out smoother

This is a quick visual to look at the effects of averaging of each weighted 
image across the week compared to the average of just fvalid for the week 

```{r}
# compute stack of just weekly fvalid: 
f_stack1 <- stack(rf1, rf2, rf3, rf4,
                 rf5, rf6, rf7)

mean_fronts = stackApply(f_stack1, c(1,1,1,1,1,1,1), fun = mean)

# also add smoother to mean_fronts for comparison
kern.weekly.fvalid = raster.gaussian.smooth(mean_fronts, sigma = 2,
                                            n = 5, type = mean)


par(mfrow = c(2,2))
plot(mean_fronts, main= "Fvaild: Fronts w/out smoother") 
plot(mean_kern, main = 'Pfront: Fronts w/smoother')
plot(kern.weekly.fvalid, main= "Weekly Fvaild: Fronts w/smoother applied after") 

```



### Nantucket Shoals

```{r}
# xmin, xmax, ymin, ymax
extent(kern.weekly.fvalid)
n.shoals <- extent(-72.0, -68.0, 38.0, 42.0)
rc.shoals <- crop(kern.weekly.fvalid, n.shoals)	

n.shoals.zoom <- extent(-72.0, -68.0, 40.0, 42.0)
rc.shoals.zoom <- crop(kern.weekly.fvalid, n.shoals.zoom)	

par(mfrow = c(2,2))
plot(rc.shoals, main = 'Nantucket Shoals')
plot(rc.shoals.zoom)


```

### EPU's 



```{r}
library(rgdal)
# get EPU shape files 
wd = here::here('shape_files/')
epu <- readOGR(wd,'EPU_NOESTUARIES')
plot(epu)
# -- Create a map with bathymetry and EPUs -- #

# atl <- marmap::getNOAA.bathy(-77.99496,-62.0023 , 34.00504, 46.00206 )
# atl = fortify.bathy(atl)
# blues = colorRampPalette(brewer.pal(9,'Blues'))(25)
# blues2 <- blues[c(5,7,9,11,13,24)]
# depths <- c(0,50,100,200,300,Inf)
# proj4string(US.areas) <- CRS("+init=epsg:4326")
# proj4string(canada.areas) <- CRS("+init=epsg:4326")
# US.areas <- US.areas %>% st_as_sf()
# canada.areas <- canada.areas %>% st_as_sf()
# proj4string(epu) <- CRS("+init=epsg:4326")
#epu <- epu %>% st_as_sf()
ggplot() +
  geom_contour_filled(data = atl,
                      aes(x=x,y=y,z=-1*z),
                      breaks=c(0,50,100,200,300,500,Inf),
                      size=c(0.3)) + 
  scale_fill_manual(values = blues2, 
                    name = paste("Depth (m)"),
                    labels = depths) +
  geom_sf(data = epu %>% st_as_sf(),
          fill = c('blue', 'green', 'lightgreen', 'turquoise'), 
          colour = 'black', alpha = 0.5) +
  geom_sf(data=US.areas) +
  geom_sf(data=canada.areas) +
  coord_sf(xlim = c(-77.99496,-63.00), 
           ylim = c(34.50,46.00),
           datum = sf::st_crs(4326))+ 
  theme_bw()
```




```{r}
epu@data
mab <- epu[na.omit(epu@data$EPU == 'MAB'),]
gom <-  epu[na.omit(epu@data$EPU == 'GOM'),]
gb <-  epu[na.omit(epu@data$EPU == 'GB'),]
plot(epu, xaxt = 'n', yaxt = 'n')
plot(gom, col = 'slateblue', add = TRUE)
plot(gb, col = 'goldenrod3', add = TRUE)
plot(mab, col = 'orangered', add = TRUE)
fnhood_mab_wk12 <-  raster::extract(ww_fnhood_202112, mab, weights = FALSE, 
                             fun = NULL, na.rm = TRUE)

fnhood_mab_wk12_crop <- raster::crop(x = ww_fnhood_202112, y = mab)
plot(fnhood_mab_wk12_crop, main = 'MAB 2021 week 12')
fnhood_mab_wk14_crop <- raster::crop(x = ww_fnhood_202114, y = mab)
plot(fnhood_mab_wk14_crop, main = 'MAB 2021 week 14')
fnhood_gom_wk12_crop <- raster::crop(x = ww_fnhood_202112, y = gom)
plot(fnhood_gom_wk12_crop, main = 'GOM 2021 week 12')
fnhood_gb_wk12_crop <- raster::crop(x = ww_fnhood_202112, y = gb)
plot(fnhood_gb_wk12_crop, main = 'GB 2021 week 12')
```



### Interannual variability in seasonal front frequency 



```{r}







```












### Example from the functions vingette 


```{r}
r <- raster(nrows=500, ncols=500, xmn=571823, xmx=616763, 
               ymn=4423540, ymx=4453690)
proj4string(r) <- crs("+proj=utm +zone=12 +datum=NAD83 +units=m +no_defs")
r[] <- runif(ncell(r), 1000, 2500)
r <- focal(r, focalWeight(r, 150, "Gauss") )
 
 # Calculate Gaussian smoothing with sigma(s) = 1-4
 g1 <- raster.gaussian.smooth(r, sigma=1, nc=11)
 g2 <- raster.gaussian.smooth(r, sigma=2, nc=11)
 g3 <- raster.gaussian.smooth(r, sigma=3, nc=11)
 g4 <- raster.gaussian.smooth(r, sigma=4, nc=11)

par(mfrow=c(2,2)) 
  plot(g1, main="Gaussian smoothing sigma = 1") 
  plot(g2, main="Gaussian smoothing sigma = 2")
  plot(g3, main="Gaussian smoothing sigma = 3")
  plot(g4, main="Gaussian smoothing sigma = 4")
```

### Loop to do all files 


```{r}
# weekly sst anomalies #
path = '/nadata/PROJECTS/IDL_PROJECTS/ILLEX_INDICATORS/R_SCRIPTS/SST_ANOM/NETCDFS/'
path = here::here('nc_files/')
files <- list.files(path = path, pattern = glob2rx('W_*.nc'), full.names = TRUE)
setwd('C:/Users/sarah.salois/Documents/github/ssalois1/frontal_metrics/rasters')
threshold = 0.4 # threshold for classifying front
for (i in 1:length(files)) {
  nc <- nc_open(files[i])  # Open files
  lat <- ncvar_get(nc, 'latitude')
  lon <- ncvar_get(nc, 'longitude')
  grad <- ncvar_get(nc, attributes(nc$var)$names[2])
  nc_close(nc)
  rm(nc)
  grad[grad < threshold] <- 0 # set all values < thresh == 0 
  for (j in 1:1){
  tmp <- (grad[,,j])
  tmp <- t(tmp) # needs to be transposed 
  # create a raster 
  r = raster(tmp, xmn = min(lon), xmx = max(lon), 
             ymn = min(lat), ymx = max(lat),
             crs = CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs+ towgs84=0,0,0"))
  r = flip(r,2) # flip it to correct orientation
  s = raster::stack(r)
  for (k in 2:7){
    tmp <- (grad[,,k])
    tmp <- t(tmp) # needs to be transposed 
    # create a raster 
    r = raster(tmp, xmn = min(lon), xmx = max(lon), 
               ymn = min(lat), ymx = max(lat),
               crs = CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs+ towgs84=0,0,0"))
    r = flip(r,2) # 
    s[[k]]= r
  }
 }  
  f_stack = stackApply(s, c(1,1,1,1,1,1,1), fun = mean)
  assign(paste0('ww_fvalid',i), f_stack)  
  # also add smoother to mean_fronts for comparison
  assign(paste0('ww_fnhood_2021',i), raster.gaussian.smooth(f_stack, 
                                                       sigma = 2,
                                                       n = 5,
                                                       type = mean))
  
  }




image(s[[8]])
image(ww_gradsst)
image(kern.weekly.fvalid)
image(ww_fnhood3)
```










## Different approach using a package with more functionality 
The mmand R package provides tools for performing mathematical morphology 
operations, such as erosion and dilation, or finding connected components,
on arrays of arbitrary dimensionality. It can also smooth and resample arrays, 
obtaining values between pixel centres or scaling the image up or down wholesale.

All of these operations are underpinned by three powerful functions, which perform different types of kernel-based operations: morph(), components() and resample().
```{r}
library(mmand)
library(loder)
# these are some examples from vignette 
fan <- readPng(system.file("images", "fan.png", package="mmand"))
display(fan)
display(gaussianSmooth(fan, c(3,3)))
display(gaussianSmooth(fan, 2))
k <- shapeKernel(c(3,3), type="box")
display(medianFilter(fan, k))

```


```{r, eval=FALSE}

fpng <- readPng('raster_fronts_day4.png')
display(fpng)
display(gaussianSmooth(fpng, .02))



```




```{r, eval=FALSE}
library(landscapemetrics)
library(landscapetools)
# landscape raster
show_landscape(rf5, discrete = TRUE)



```
