---
title: "choosing_frontal_neighborhood"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      warning = FALSE,
                      message = FALSE)
```

## R Markdown


```{r }
library(raster)
library(RColorBrewer)
library(ncdf4)
library(wesanderson)
# library(terra) trying to stick to raster (though it will be depreciated)
```


```{r }

## Color Palette
# Continuous palette for displaying smoother images
cols = rev(brewer.pal(11,'RdYlBu'))
pal <- colorRampPalette(cols)(30)
jet.colors <-colorRampPalette(c("blue", "#007FFF", "cyan","#7FFF7F", "yellow", "#FF7F00", "red", "#7F0000"))

## Getting files
## week 20 and 42 are good weeks in modis 
path = here::here('nc_files/ww')
# The modis files (WW_) do not have x,y component - just full metrics, 
# so need to select the W_ for now, which is the 7 daily files for a given week
files <- list.files(path = path, pattern = glob2rx('W_202120*.nc'), 
                    full.names = TRUE)

```


## Data

Pulling in the data 

### Modis
```{r}
## Modis

nc <- nc_open(files[1])  # Open files
lat <- ncvar_get(nc, 'latitude')
lon <- ncvar_get(nc, 'longitude')
sst <- ncvar_get(nc, attributes(nc$var)$names[1])
grad.m <- ncvar_get(nc, attributes(nc$var)$names[2])
x.m <- ncvar_get(nc, attributes(nc$var)$names[3])
y.m <- ncvar_get(nc, attributes(nc$var)$names[4])
nc_close(nc)
rm(nc)
```



## Stacking rasters 

### Modis 


Trying this with raster package: 


```{r}

# ## Modis
# ra.grad.m <- list()
# ra.xcomp.m <- list()
# ra.ycomp.m <- list()
# ra.front.m <- list()
# #threshold = 0.18 # this is for static threshold method, not focal method
# # for (i in 1:52){ will need when fixed
# for (i in 1:7){
#   tmp.g <- (grad.m[,,i]) 
#   tmp.gt <- t(tmp.g) 
#   r.g = raster(tmp.gt, xmn = min(lon), xmx = max(lon), 
#                ymn = min(lat), ymx = max(lat),
#                crs = CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs+ towgs84=0,0,0"))
#   r.g = raster::flip(r.g,2)  
#   #plot(r.g, col = pal)
#   assign(paste('r.g.',i, sep = ''), r.g)
#   ra.grad.m[[i]] <- get(paste0('r.g.',i))
#   tmp.x <- (x.m[,,i]) 
#   tmp.xt <- t(tmp.x)
#   r.x = raster(tmp.xt, xmn = min(lon), xmx = max(lon), 
#                ymn = min(lat), ymx = max(lat),
#                crs = CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs+ towgs84=0,0,0"))
#   r.x = raster::flip(r.x,2)  
#   assign(paste('r.x.',i, sep = ''), r.x)
#   ra.xcomp.m[[i]] <- get(paste0('r.x.',i))
#   tmp.y <- (y.m[,,i]) 
#   tmp.yt <- t(tmp.y)
#   r.y = raster(tmp.yt, xmn = min(lon), xmx = max(lon), 
#                ymn = min(lat), ymx = max(lat),
#                crs = CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs+ towgs84=0,0,0"))
#   r.y = raster::flip(r.y,2)  
#   assign(paste('r.y.',i, sep = ''), r.y)
#   ra.ycomp.m[[i]] <- get(paste0('r.y.',i))
#   # Change this to reflect new front detection method
#   # tmp.f <- (grad.m[,,i])
#   # tmp.f[tmp.f < threshold] <- 0
#   # tmp.ft <- t(tmp.f)
#   # r.f = raster(tmp.ft, xmn = min(lon), xmx = max(lon),
#   #              ymn = min(lat), ymx = max(lat),
#   #              crs = CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs+ towgs84=0,0,0"))
#   # r.f = raster::flip(r.f,2)
#   # plot(r.f, col = pal)
#   # assign(paste('r.f.',i, sep = ''), r.f)
#   # ra.front.m[[i]] <- get(paste0('r.f.',i))
# }
# 

ra.front.m <- list()
for (i in 1:7){
 # This reflects new front detection method
  i=1
  tmp.f <- (grad.m[,,i])
  tmp.ft <- t(tmp.f)
  r.f = raster(tmp.ft, xmn = min(lon), xmx = max(lon),
               ymn = min(lat), ymx = max(lat),
               crs = CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs+ towgs84=0,0,0"))
  #r.f.bt = raster::flip(r.f,2)
  r.f = raster::flip(r.f,2)
  plot(r.f, col = pal)
  #plot(r.f.bt, col = pal)
  r.f.og <- r.f
  tmp.foc <- raster::focal(r.f, fun=mean, 
                           na.rm=TRUE, w=matrix(1/9,nrow=3,ncol=3))
  
  r.f[r.f >= tmp.foc] <- r.f
  id_raster_sub <- id_raster[[1]]>2
  catch_raster_sub <- mask(catch_raster,id_raster_sub/id_raster_sub)

  assign(paste('r.f.',i, sep = ''), r.f)
  ra.front.m[[i]] <- get(paste0('r.f.',i))
  
}
  #r.f[r.f >= tmp.foc] <- r.f
  id_raster_sub <- id_raster[[1]]>2
  catch_raster_sub <- mask(catch_raster,id_raster_sub/id_raster_sub)
  assign(paste('r.f.',i, sep = ''), r.f)
  ra.front.m[[i]] <- get(paste0('r.f.',i))
  


# front.stack.f.rasterpackage <- stack(ra.front.m)
#   r.f.t <- ifelse(r.f <= tmp.foc, 0,r.f)
#   r.f.t <- r.f <= tmp.foc
# # remove from r1(stack of x) all values that are NA in r3(stack of fronts)
# r.f.mask <- raster::mask(r.f,tmp.foc)
# foc.df <- as.data.frame(tmp.foc, xy = TRUE) # this works with Raster* objects as well
# foc.df$layer[is.nan(foc.df$layer)]<-NA
# front.df <- as.data.frame(r.f, xy = TRUE) # this works with Raster* objects as well
# locs.rm.front <- which(na.omit(front.df$layer) >= na.omit(foc.df$layer))
# front.df.foc <- front.df[locs.rm.front,]
# rrr = rasterFromXYZ(front.df.foc)  
# r.f.subs <- subs(r.f,foc.df)


```


```{r}


tmp.foc2 <- raster::focal(r.f.og, fun = mean, 
                         na.rm = TRUE, 
                         w = matrix(1/9, nrow = 3, ncol = 3))
tmp.foc3 <- raster::focal(r.f.og, fun = median, 
                          na.rm = TRUE, 
                          w = matrix(1/9, nrow = 3, ncol = 3))

tmp.foc4 <- raster::focal(r.f.og, fun = mean, 
                          na.rm = TRUE, 
                          w = matrix(1/9, nrow = 5, ncol = 5))
tmp.foc5 <- raster::focal(r.f.og, fun = median, 
                          na.rm = TRUE, 
                          w = matrix(1/9, nrow = 5, ncol = 5))

# thresh <- r.f.og >= tmp.foc5
# fronts <- mask(r.f.og,thresh/thresh)
# plot(fronts, col = pal)
# plot(r.f.og)
# plot(tmp.foc)

```


```{r}
par(mfrow = c(2,2))
plot(tmp.foc2, main = 'mean focal 3x3', col = pal)
plot(tmp.foc3, main = 'median focal 3x3', col = pal)
plot(tmp.foc4, main = 'mean focal 5x5', col = pal)
plot(tmp.foc5, main = 'median focal 5x5', col = pal)
```





```{r}
thresh <- r.f.og >= tmp.foc5
#plot(thresh, col = pal)
fronts <- mask(r.f.og,thresh/thresh)

par(mfrow = c(2,2))
plot(r.f.og, main = 'grad mag', col = pal)
plot(tmp.foc5, main = 'focal stats (sets threshold)', col = pal)
#plot(tmp.foc3, main = 'larger focal', col = pal)
plot(thresh, main = 'threshold raster', col = pal)
plot(fronts, main = 'fronts (grad mad >= threshold', col = pal)


```





```{r}

tmp.foc.mean <- raster::focal(r.f.og, fun = mean, 
                         na.rm = TRUE, 
                         w = matrix(1,3,3))

tmp.foc.median <- raster::focal(r.f.og, fun = median, 
                         na.rm = TRUE, 
                          w = matrix(1,3,3))
r.f.max <- r.f.og
r.f.max[is.na(r.f.max)] <- 0
tmp.foc.max <- raster::focal(r.f.max, fun = na.omit(max), 
                         na.rm = TRUE, 
                          w = matrix(1,3,3))

par(mfrow = c(2,2))
plot(r.f.og, main = 'grad mag', col = pal)
plot(tmp.foc.mean, main = 'focal stats mean', col = pal)
plot(tmp.foc.median, main = 'focal stats median', col = pal)
plot(tmp.foc.max, main = 'focal stats max', col = pal)






```





```{r}
thresh.mean <- r.f.og >= tmp.foc.mean
fronts.mean <- mask(r.f.og,thresh.mean/thresh.mean)
thresh.median <- r.f.og >= tmp.foc.median
fronts.median <- mask(r.f.og,thresh.median/thresh.median)
thresh.max <- r.f.og >= tmp.foc.max
thresh.max2 <- r.f.og > tmp.foc.max
fronts.max <- mask(r.f.og,thresh.max/thresh.max)

thresh = tmp.foc.max/tmp.foc.max


par(mfrow = c(2,2))
plot(r.f.og, main = 'grad mad', col = pal)
plot(fronts.mean, main = 'fronts (grad mad >= mean', col = pal)
plot(fronts.median, main = 'fronts (grad mad >= median', col = pal)
plot(fronts.max, main = 'fronts (grad mad >= max', col = pal)
plot(thresh.median, col = pal)

```






Midrange Threshold on real grad-sst

```{r}
# ## Modis
ra.grad.m <- list()
# ra.xcomp.m <- list()
# ra.ycomp.m <- list()
# ra.front.m <- list()

for (i in 1:7){
  tmp.g <- (grad.m[,,i])
  tmp.gt <- t(tmp.g)
  r.g = raster(tmp.gt, xmn = min(lon), xmx = max(lon),
               ymn = min(lat), ymx = max(lat),
               crs = CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs+ towgs84=0,0,0"))
  r.g = raster::flip(r.g,2)
  plot(r.g, col = pal)
  assign(paste('r.g.',i, sep = ''), r.g)
  ra.grad.m[[i]] <- get(paste0('r.g.',i))
}
# sst
i=2
 tmp.s <- (sst[,,i])
  tmp.st <- t(tmp.s)
  r.s = raster(tmp.st, xmn = min(lon), xmx = max(lon),
               ymn = min(lat), ymx = max(lat),
               crs = CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs+ towgs84=0,0,0"))
  r.s = raster::flip(r.s,2)
  plot(r.s, col = pal)
  
fronts.t1.r.g.2.9 <- r.g.2
fronts.t2.r.g.2.9 <- r.g.2
fronts.old <- r.g.2

## Generate threshold and then apply 
thresh.part1.9 <- raster::focal(r.g.2, fun = function (x){(max(x)+min(x))/2}, 
                        w = matrix(1,9,9))
fronts.t1.r.g.2.9[fronts.t1.r.g.2.9 < thresh.part1.9] <- NA
range(na.omit(thresh.part1.9@data@values))

## Set up secondary filtration 
thresh.part2.9 <- median(na.omit(thresh.part1.9@data@values))
fronts.t2.r.g.2.9[fronts.t2.r.g.2.9 < thresh.part2.9] <- NA
fronts.old[fronts.old < 0.15] <- NA
## note: I added .9 to reduce the neighborhood size
# Plot all to see 
plot(r.s, main='SST, 2021 wk 20', col = pal) # sst 
plot(r.g.2, main='Grad SST, 2021 wk 20', col = pal) # grad
plot(thresh.part1.9, main='Midrange threshold, step 1', col = pal)
plot(thresh.part2, main='Midrange threshold, step 2', col = pal)
plot(fronts.t1.r.g.2, main='Fronts after Midrange threshold, step 1', 
     col = pal)
plot(fronts.t2.r.g.2, main='Fronts after Midrange threshold, step 2', 
     col = pal)
plot(fronts.old, col = pal, main = 'Our arbitraty threshold we originially chose for our region')
plot(fronts.t1.r.g.2.9, main='Fronts after Midrange threshold, step 1 (9x9)', 
     col = pal)
plot(fronts.t2.r.g.2.9, main='Fronts after Midrange threshold, step 2 (9x9)', 
     col = pal)
```






Testing on a new data set - ACSPO
```{r}
# Pull in data file from the ACSPO SST 
nc <- nc_open(here::here('nc_files/ww/WW_202101_202152-ACSPO-V2.0-NESGRID-GRAD_SST-BOA-STACKED_STATS.nc'))  # Open files
lat <- ncvar_get(nc, 'latitude')
lon <- ncvar_get(nc, 'longitude')
sst.ac <- ncvar_get(nc, attributes(nc$var)$names[4])
grad.ac <- ncvar_get(nc, attributes(nc$var)$names[1])
x.ac <- ncvar_get(nc, attributes(nc$var)$names[2])
y.ac <- ncvar_get(nc, attributes(nc$var)$names[3])
nc_close(nc)
rm(nc)

```

```{r}
image(sst.ac[,,1])
image(sst.ac[,,2])
image(sst.ac[,,14])
image(sst.ac[,,35])
image(sst.ac[,,41])
image(sst.ac[,,51])
```




```{r}
# select one day and create a raster for testing thresholds
# SST for comparison 
tmp.sst <- sst.ac[,,1]
tmp.sst <- t(tmp.sst)
sst.r = raster(tmp.sst, xmn = min(lon), xmx = max(lon),
               ymn = min(lat), ymx = max(lat),
               crs = CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs+ towgs84=0,0,0"))
sst.r = raster::flip(sst.r,2)

 

# Grad Mag
tmp.grad <- grad.ac[,,20]
tmp.grad <- t(tmp.grad)
grad.r = raster(tmp.grad, xmn = min(lon), xmx = max(lon),
               ymn = min(lat), ymx = max(lat),
               crs = CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs+ towgs84=0,0,0"))
grad.r = raster::flip(grad.r,2)
  
 

  
plot(sst.r, col = pal, main = 'ACSPO SST')
plot(grad.r, col = pal, main = 'ACSPO GRAD MAG')
  
```


Testing threshold: 


```{r}
## Generate threshold and then apply 

fronts.part1.acspo <- grad.r
fronts.part2.acspo <- grad.r
fronts.old <- grad.r

thresh.part1.9 <- raster::focal(grad.r, fun = function (x){(max(x)+min(x))/2}, 
                        w = matrix(1,9,9))
fronts.part1.acspo[fronts.part1.acspo < thresh.part1.9] <- NA
range(na.omit(thresh.part1.9@data@values))

## Set up secondary filtration 
thresh.part2.9 <- median(na.omit(thresh.part1.9@data@values))
fronts.part2.acspo[fronts.part2.acspo < thresh.part2.9] <- NA
fronts.old[fronts.old < 0.15] <- NA
```


```{r}
## note: any object with a .9 is the 9x9 neighborhood size
# Plot all to see 
plot(sst.r, main='SST ACSPO 2021', col = pal) # sst 
plot(grad.r, main='Grad Mag ACSPO 2021', col = pal) # grad
plot(thresh.part1.9, main='Midrange threshold, step 1', col = pal)
# plot(thresh.part2, main='Midrange threshold, step 2', col = pal)
# plot(fronts.part1.acspo, main='Fronts after Midrange threshold, step 1', 
#      col = pal)
# plot(fronts.part2.acspo, main='Fronts after Midrange threshold, step 2', 
#      col = pal)
plot(fronts.part1.acspo, main='Fronts after Midrange threshold, step 1 (9x9)', 
     col = pal)
plot(fronts.part2.acspo, main='Fronts after Midrange threshold, step 2 (9x9)', 
     col = pal)
plot(fronts.old, col = pal, 
     main = 'Our arbitraty threshold we originially chose for our region')

```


Daily - stack these and perform metrics


```{r}
# Pull in data file from the ACSPO SST 
nc <- nc_open(here::here('nc_files/dd/DD_20210101_20211231-ACSPO-V2.0-NESGRID-GRAD_SST-BOA.nc'))  # Open files
lat <- ncvar_get(nc, 'latitude')
lon <- ncvar_get(nc, 'longitude')
grad.dd <- ncvar_get(nc, attributes(nc$var)$names[1])
x.dd <- ncvar_get(nc, attributes(nc$var)$names[2])
y.dd <- ncvar_get(nc, attributes(nc$var)$names[3])
#sst.ac <- ncvar_get(nc, attributes(nc$var)$names[4]) ## SST not in these files
nc_close(nc)
rm(nc)
```


Prep data to run metrics - trying on just one week of daily data

```{r}
## ACSPO SST
grad <- list()
xcomp <- list()
ycomp <- list()
front.p1 <- list()
front.p2 <- list()
#front.oldthresh <- list()
# going to try days 136:142 hoping this week of may 16 2021, day 136(Sun) 137 (Mon)
for (i in 136:143){
  tmp.g <- (grad.dd[,,i]) # iterating through each day of week 20
  tmp.gt <- t(tmp.g)
  r.g = raster(tmp.gt, xmn = min(lon), xmx = max(lon),
               ymn = min(lat), ymx = max(lat),
               crs = CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs+ towgs84=0,0,0"))
  r.g = raster::flip(r.g,2)
  #plot(r.g, col = pal)
  assign(paste('r.g.',i, sep = ''), r.g)
  grad[[i]] <- get(paste0('r.g.',i)) # storing this in a list to stack later
  tmp.x <- (x.dd[,,i]) 
  tmp.xt <- t(tmp.x)
  r.x = raster(tmp.xt, xmn = min(lon), xmx = max(lon),
               ymn = min(lat), ymx = max(lat),
               crs = CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs+ towgs84=0,0,0"))
  r.x = raster::flip(r.x,2)
  assign(paste('r.x.',i, sep = ''), r.x)
  xcomp[[i]] <- get(paste0('r.x.',i))
  tmp.y <- (y.dd[,,i])
  tmp.yt <- t(tmp.y)
  r.y = raster(tmp.yt, xmn = min(lon), xmx = max(lon),
               ymn = min(lat), ymx = max(lat),
               crs = CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs+ towgs84=0,0,0"))
  r.y = raster::flip(r.y,2)
  assign(paste('r.y.',i, sep = ''), r.y)
  ycomp[[i]] <- get(paste0('r.y.',i))
  ## This reflects new 2-step dynamic local front detection method
  tmp.fp1 <- r.g   # (grad.dd[,,i]) # setting up grad_mag raster for 1st filter
  tmp.fp2 <- r.g  # setting up gradient_mag raster for second filter 
 # fronts.old <- r.g
  thresh.part1.9 <- raster::focal(r.g, fun = function (x){(max(x)+min(x))/2}, 
                        w = matrix(1,15,15)) # change 9 to 15, not changing names
  tmp.fp1[tmp.fp1 < thresh.part1.9] <- NA
  # range(na.omit(thresh.part1.9@data@values)) # checking values
  ## Set up secondary filtration 
  thresh.part2.9 <- median(na.omit(thresh.part1.9@data@values))
  tmp.fp2[tmp.fp2 < thresh.part2.9] <- NA
  # Compare to old
  # fronts.old[fronts.old < 0.18] <- NA
  # plot(r.f, col = pal)
  assign(paste('r.f1.',i, sep = ''), tmp.fp1)
  assign(paste('r.f2.',i, sep = ''), tmp.fp2)
  # assign(paste('r.fold.',i, sep = ''), fronts.old)
  front.p1[[i]] <- get(paste0('r.f1.',i))
  front.p2[[i]] <- get(paste0('r.f2.',i))
  # front.oldthresh[[i]] <- get(paste0('r.fold.',i))
}

# will need to stack the raster layers in each list

```

Plotting to check before I start metrics

9 x 9 kernel 
```{r}
plot(r.g, main='Grad Mag ACSPO 2021', col = pal) # grad
plot(r.f1.136, main='Fronts after Midrange threshold, step 1 (9x9)', 
     col = pal)
plot(r.f2.136, main='Fronts after Midrange threshold, step 2 (9x9)', 
     col = pal)
plot(fronts.old, col = pal, 
     main = 'Our arbitraty threshold we originially chose for our region')

```


15 x 15 kernel 

```{r}
plot(r.g, main='Grad Mag ACSPO 2021', col = pal) # grad
plot(r.f1.136, main='Fronts after Midrange threshold, step 1 (15x15)', 
     col = jet.colors(30))
plot(r.f2.136, main='Fronts after Midrange threshold, step 2 (15x15)', 
     col = pal)
plot(fronts.old, col = pal, 
     main = 'Our arbitraty threshold we originially chose for our region')

```

## Stacking 
Need to stack the images by temporal resolution of interest

```{r}

# -- stack static threshold -- # 
grad.stack <- raster::stack(grad[136:143])
front.stack <- raster::stack(front.p2[136:143])
x.stack<- raster::stack(xcomp[136:143])
y.stack <- raster::stack(ycomp[136:143])


# Cleaning up environment - too many large files 
rm(list = grep("tmp", ls(), value = TRUE))
rm(list = grep("r.x.", ls(), value = TRUE))
rm(list = grep("r.g.", ls(), value = TRUE))
rm(list = grep("r.y.", ls(), value = TRUE))
rm(list = grep("r.f.", ls(), value = TRUE))


```



```{r}
## Functions
fx.sum.greater.than.zero <- function(x) sum(na.omit(x > 0))
fx.sum <- function(x) sum(na.omit(x))
fx.sumsqrs <- function(x) {sum((na.omit(x) - mean(na.omit(x)))^2)}
# create an if-else reclassify statement
rc <- function(x1) {
  ifelse(x1 <= pers_thresh, 1, 
         ifelse((x1 > pers_thresh), 0))
}
```


```{r}
# Metrics

# Set threshold for low temporal variability 
#pers_thresh <- 0.08 # original 
pers_thresh <- 0.3
## Initialize these
r1 = x.stack # stack of x
r3 = front.stack # stack of fronts
# r3[r3 <= 0] <- NA # do I need to do this? - yes for mask*, not with new front rasters
# plot(r3, col = jet.colors(5),  main = 'fronts NA')
# remove from r1(stack of x) all values that are NA in r3(stack of fronts)
r4 <- raster::mask(r1, r3)
#plot(r4, col = jet.colors(5), main = 'x based on grad mag')
r5 = y.stack # stack of y
r6 <- raster::mask(r5, r3)
plot(r6, col = pal, main = 'y based on grad mag')
## Base params
fvalid <- calc(front.stack, fx.sum.greater.than.zero)
m_sum <- calc(front.stack, fx.sum)
fclear_m <- calc(grad.stack, fx.sum.greater.than.zero)
# x_var
x_based_on_mag <- r4
x_sum <- calc(x_based_on_mag, fx.sum)
x_sumsqr <- calc(x_based_on_mag, fx.sumsqrs)
# y_var
y_based_on_mag <- r6
y_sum <- calc(y_based_on_mag, fx.sum)
y_sumsqr <- calc(y_based_on_mag, fx.sumsqrs)
# Metrics
fmean = (sqrt((x_sum/fvalid)^2 + (y_sum/fvalid)^2))
fvar = (x_sumsqr + y_sumsqr)/fvalid
fsd = sqrt(fvar)
fcv = fsd/fmean
fprob = fvalid/fclear_m
fintst = fmean * fprob
fpers <- overlay(fsd, fun=rc)
fpersprob = fpers * fprob
```

Plotting metrics using focal threshold with raster package instead of terra

```{r}

pdf(file = 'metrics_focal_front_wk_20_2021_acspo_sst.pdf',
    width = 10, height = 6)
par(mfrow = c(2,5), oma = c(1,1,1,1))
plot(grad.r, main = 'ACSPO GRAD MAG', col = jet.colors(25))
plot(fvalid, main = 'Fvalid', col= jet.colors(20))
plot(fclear_m, main = 'Fclear', col= jet.colors(20))
plot(fmean, main = 'Frontal Mean', col= jet.colors(25))
plot(fprob, main = 'Frontal Probability', col= jet.colors(25))
plot(fvar, main = 'Frontal Variance', col= jet.colors(25))
plot(fsd, main = 'Frontal Standard Deviation', col= jet.colors(25))
plot(fcv, main = 'Frontal CV', col= jet.colors(25))
plot(fintst, main = 'Frontal Intensity', col= jet.colors(20))
plot(fpers, main = 'Frontal Persistence', col= jet.colors(25))
plot(fpersprob, main = 'Persistence Probability', col = jet.colors(25))
dev.off()


```



```{r}
range(na.omit(fsd@data@values))

# pers_thresh <- 0.3
# fpers <- overlay(fsd, fun=rc)
# fpersprob = fpers * fprob
plot(fpers, main = 'Frontal Persistence', col= jet.colors(25))
plot(fpersprob, main = 'Persistence Probability', col = jet.colors(25))
plot(fprob, main = 'Frontal Probability', col= jet.colors(25))


```



```{r}
pdf(file = 'persprob_focal_front_wk_20_2021_acspo_sst.pdf',
    width = 8, height = 5)
par(mfrow = c(1,2), oma = c(1,1,1,1), mar = c(2, 3, 3, 2))
plot(fprob, main = 'Frontal Probability', col= jet.colors(25))
plot(fpersprob, main = 'Persistence Probability, thresh = 0.3', col = jet.colors(25))
dev.off()

```







