---
title: "Comparing threshold methods"
author: "Sarah Salois"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

## Setting up

```{r }
library(raster)
library(RColorBrewer)
library(ncdf4)
library(wesanderson)
library(terra)

## Functions
fx.sum.greater.than.zero <- function(x) sum(na.omit(x > 0))
fx.sum <- function(x) sum(na.omit(x))
fx.sumsqrs <- function(x) {sum((na.omit(x) - mean(na.omit(x)))^2)}
# create an if-else reclassify statement
rc <- function(x1) {
  ifelse(x1 <= pers_thresh, 1, 
         ifelse((x1 > pers_thresh), 0))
}
## Color Palette
# Continuous palette for displaying smoother images
cols = rev(brewer.pal(11,'RdYlBu'))
pal <- colorRampPalette(cols)(30)

## Getting files
## week 20 and 42 are good weeks in modis 
path = here::here('nc_files/ww')
files2 <- list.files(path = path, pattern = glob2rx('WW_2021*.nc'),
                    full.names = TRUE)
# The modis files (WW_) do not have x,y component - just full metrics, 
# so need to select the W_ for now, which is the 7 daily files for a given week
files <- list.files(path = path, pattern = glob2rx('W_202120*.nc'), 
                    full.names = TRUE)
```

## Data

Pulling in the data 

### Modis
```{r}
## Modis

nc <- nc_open(files[1])  # Open files
lat <- ncvar_get(nc, 'latitude')
lon <- ncvar_get(nc, 'longitude')
grad.m <- ncvar_get(nc, attributes(nc$var)$names[2])
x.m <- ncvar_get(nc, attributes(nc$var)$names[3])
y.m <- ncvar_get(nc, attributes(nc$var)$names[4])
nc_close(nc)
rm(nc)
```


### MUR
```{r}
## Mur
nc <- nc_open(files[1])  # Open files
lat <- ncvar_get(nc, 'latitude')
lon <- ncvar_get(nc, 'longitude')
grad.mur <- ncvar_get(nc, attributes(nc$var)$names[1])
x.mur <- ncvar_get(nc, attributes(nc$var)$names[2])
y.mur <- ncvar_get(nc, attributes(nc$var)$names[3])
nc_close(nc)
rm(nc)
```


## Stacking rasters 

### Modis 

```{r}
## Modis
ra.grad.m <- list()
ra.xcomp.m <- list()
ra.ycomp.m <- list()
ra.front.m <- list()
threshold = 0.18 # this is for static threshold method, not focal method
# for (i in 1:52){ will need when fixed
for (i in 1:7){
  tmp.g <- (grad.m[,,i]) 
  tmp.gt <- t(tmp.g) 
  r.g = raster(tmp.gt, xmn = min(lon), xmx = max(lon), 
               ymn = min(lat), ymx = max(lat),
               crs = CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs+ towgs84=0,0,0"))
  r.g = raster::flip(r.g,2)  
  #plot(r.g, col = pal)
  assign(paste('r.g.',i, sep = ''), r.g)
  ra.grad.m[[i]] <- get(paste0('r.g.',i))
  tmp.x <- (x.m[,,i]) 
  tmp.xt <- t(tmp.x)
  r.x = raster(tmp.xt, xmn = min(lon), xmx = max(lon), 
               ymn = min(lat), ymx = max(lat),
               crs = CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs+ towgs84=0,0,0"))
  r.x = raster::flip(r.x,2)  
  assign(paste('r.x.',i, sep = ''), r.x)
  ra.xcomp.m[[i]] <- get(paste0('r.x.',i))
  tmp.y <- (y.m[,,i]) 
  tmp.yt <- t(tmp.y)
  r.y = raster(tmp.yt, xmn = min(lon), xmx = max(lon), 
               ymn = min(lat), ymx = max(lat),
               crs = CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs+ towgs84=0,0,0"))
  r.y = raster::flip(r.y,2)  
  assign(paste('r.y.',i, sep = ''), r.y)
  ra.ycomp.m[[i]] <- get(paste0('r.y.',i))
  # Change this to reflect new front detection method
  tmp.f <- (grad.m[,,i])
  tmp.f[tmp.f < threshold] <- 0
  tmp.ft <- t(tmp.f)
  r.f = raster(tmp.ft, xmn = min(lon), xmx = max(lon),
               ymn = min(lat), ymx = max(lat),
               crs = CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs+ towgs84=0,0,0"))
  r.f = raster::flip(r.f,2)
  plot(r.f, col = pal)
  assign(paste('r.f.',i, sep = ''), r.f)
  ra.front.m[[i]] <- get(paste0('r.f.',i))
}


```




Trying focal frontal threshold 
```{r}
# Modis
# --- need to convert all to a spat-raster --- # 
sr.grad.m <- list()
sr.xcomp.m <- list()
sr.ycomp.m <- list()
sr.focal.front.m <- list()
# for (i in 1:52){ will need when fixed
for (i in 1:7){
  # gradient magnitude
  tmp.g <- (grad.m[,,i])
  tmp.gt <- t(tmp.g)
  r.g = rast(tmp.gt, crs = "EPSG:4326")
  r.g = terra::flip(r.g, direction ='v')
  plot(r.g, col = pal, main = 'grad_sst')
  assign(paste('r.g.',i, sep = ''), r.g)
  sr.grad.m[[i]] <- get(paste0('r.g.',i)) # list all rasters to stack after
  # x component
  tmp.x <- (x.m[,,i])
  tmp.xt <- t(tmp.x)
  r.x = rast(tmp.xt, crs = "EPSG:4326")
  r.x = terra::flip(r.x, direction ='v')
  assign(paste('r.x.',i, sep = ''), r.x)
  sr.xcomp.m[[i]] <- get(paste0('r.x.',i))
  # y component
  tmp.y <- (y.m[,,i])
  tmp.yt <- t(tmp.y)
  r.y = rast(tmp.yt, crs = "EPSG:4326")
  r.y = terra::flip(r.y, direction ='v')
  assign(paste('r.y.',i, sep = ''), r.y)
  sr.ycomp.m[[i]] <- get(paste0('r.y.',i))
 # This reflects new front detection method
  tmp.f <- (grad.m[,,i])
  tmp.ft <- t(tmp.f)
  r.f <- rast(tmp.ft, crs = "EPSG:4326") 
  r.f <- terra::flip(r.f, direction ='v')  
  tmp.foc <- terra::focal(r.f, w = 3, fun = 'mean')
  r.f[r.f <= tmp.foc] <- 0
  plot(r.f, col = pal, main = 'fronts')
  assign(paste('r.f.',i, sep = ''), r.f)
  sr.focal.front.m[[i]] <- get(paste0('r.f.',i))
}



# ## S4 method for signature 'SpatRaster'
# spat.rast.grad <- rast(grad.m) 
# tmp.spat.rast.gradt <- t(spat.rast.grad) 
# tmp.spat.rast.gradtf = terra::flip(tmp.spat.rast.gradt, direction ='v')  
# tmp.foc <- terra::focal(tmp.spat.rast.gradtf, w = 3, fun = 'mean')
# plot(tmp.foc, col = pal)
# 
# # maybe try this on one raster instead of all layers
#  # Change this to reflect new front detection method
#   tmp.f <- (grad.m[,,i])
#   tmp.ft <- t(tmp.f)
#   r.f <- rast(tmp.ft) 
#   r.f <- terra::flip(r.f, direction ='v')  
#   tmp.foc <- terra::focal(r.f, w = 3, fun = 'mean')
#   r.f <- r.f[r.f < tmp.foc] <- 0
#   assign(paste('r.f.',i, sep = ''), r.f)
#   r.focal.front.m[[i]] <- get(paste0('r.f.',i))
# rm(list = grep("r.g.", ls(), value = TRUE))
# rm(list = grep("r.x.", ls(), value = TRUE))
# rm(list = grep("r.y.", ls(), value = TRUE))
# rm(list = grep("r.f.", ls(), value = TRUE))
# rm(list = grep('tmp.', ls(), value = TRUE))

```



### MUR

```{r}
## MUR
#threshold = 0.18 # threshold for classifying front at 2km (0.15-0.18) 0.12
threshold = 0.06 # threshold for classifying front (0.06-)
r.grad.mur <- list()
r.xcomp.mur <- list()
r.ycomp.mur <- list()
r.front.mur <- list()
for (i in 1:52){
  tmp.g <- (grad.mur[,,i]) 
  tmp.gt <- t(tmp.g) 
  r.g = raster(tmp.gt, xmn = min(lon), xmx = max(lon), 
               ymn = min(lat), ymx = max(lat),
               crs = CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs+ towgs84=0,0,0"))
  r.g = raster::flip(r.g,2)  
  #plot(r.g, col = pal)
  assign(paste('r.g.',i, sep = ''), r.g)
  r.grad.mur[[i]] <- get(paste0('r.g.',i))
  tmp.x <- (x.mur[,,i]) 
  tmp.xt <- t(tmp.x)
  r.x = raster(tmp.xt, xmn = min(lon), xmx = max(lon), 
               ymn = min(lat), ymx = max(lat),
               crs = CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs+ towgs84=0,0,0"))
  r.x = raster::flip(r.x,2)  
  assign(paste('r.x.',i, sep = ''), r.x)
  r.xcomp.mur[[i]] <- get(paste0('r.x.',i))
  tmp.y <- (y.mur[,,i]) 
  tmp.yt <- t(tmp.y)
  r.y = raster(tmp.yt, xmn = min(lon), xmx = max(lon), 
               ymn = min(lat), ymx = max(lat),
               crs = CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs+ towgs84=0,0,0"))
  r.y = raster::flip(r.y,2)  
  assign(paste('r.y.',i, sep = ''), r.y)
  r.ycomp.mur[[i]] <- get(paste0('r.y.',i))
  ## Change this to reflect new front detection method
  tmp.f <- (grad.mur[,,i])
  tmp.f[tmp.f < threshold] <- 0
  tmp.ft <- t(tmp.f)
  r.f = raster(tmp.ft, xmn = min(lon), xmx = max(lon),
               ymn = min(lat), ymx = max(lat),
               crs = CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs+ towgs84=0,0,0"))
  r.f = raster::flip(r.f,2)
  assign(paste('r.f.',i, sep = ''), r.f)
  r.front.mur[[i]] <- get(paste0('r.f.',i))
}

```


## Stacking 
First need to stack the images by temporal resolution of interest

```{r}

## this works for raster
#stack.rast <- stack(r.grad.m)

# -- stack static threshold -- # 
grad.stack.s <- stack(ra.grad.m)
front.stack.s <- stack(ra.front.m)
x.stack.s <- stack(ra.xcomp.m)
y.stack.s <- stack(ra.ycomp.m)


## this works for terra
# many_rasters <- list(x,x)
# stack.rast <- rast(many_rasters)

# -- focal threshold -- # 

grad.stack.f <- terra::rast(sr.grad.m)
front.stack.f <- terra::rast(sr.focal.front.m)
x.stack.f <- terra::rast(sr.xcomp.m)
y.stack.f <- terra::rast(sr.ycomp.m)



```

```{r}
# Just cleaning up - remove the extra stacks

rm(list = grep("r.g.", ls(), value = TRUE))
rm(list = grep("r.x.", ls(), value = TRUE))
rm(list = grep("r.y.", ls(), value = TRUE))
rm(list = grep("r.f.", ls(), value = TRUE))
rm(list = grep('tmp.', ls(), value = TRUE))


rm(ra.grad.m)
rm(ra.front.m)
rm(ra.xcomp.m)
rm(ra.ycomp.m)

```



## Calculate metrics 

### Modis

#### Static threshold for frontal detection
```{r}
# Metrics
# Select a single layer (week) to test metric calculations
# sgspr <- r.grad.mur[[21]]
# sfspr <- r.front.m[[21]]
# sxspr <- r.xcomp.m[[21]]
# syspr <- r.ycomp.m[[21]]

# -- stack -- # 
# sgspr <- stack(ra.grad.m)
# sfspr <- stack(ra.front.m)
# sxspr <- stack(ra.xcomp.m)
# syspr <- stack(ra.ycomp.m)
sgspr <- grad.stack.s
sfspr <- front.stack.s
sxspr <- x.stack.s
syspr <- y.stack.s


# Set threshold for low temporal variability 
range(na.omit(sfspr))
range(na.omit(sgspr@data@values))
pers_thresh <- 0.08
## Initialize these
r1 = sxspr # stack of x
r3 = sfspr # stack of fronts
r3[r3 <= 0] <- NA # do I need to do this? - ys for mask*
plot(r3, col = pal,  main = 'fronts NA')
# remove from r1(stack of x) all values that are NA in r3(stack of fronts)
r4 <- raster::mask(r1, r3)
plot(r4, col = pal, main = 'x based on grad mag')
r5 = syspr # stack of y
r6 <- raster::mask(r5, r3)
plot(r6, col = pal, main = 'y based on grad mag')
## Base params
fvalid <- raster::calc(sfspr, fx.sum.greater.than.zero)
fvalid.test <- calc(r3, fx.sum.greater.than.zero)
m_sum <- calc(sfspr, fx.sum)
fclear_m <- calc(sgspr, fx.sum.greater.than.zero)
# x_var
x_based_on_mag <- r4
x_sum <- calc(x_based_on_mag, fx.sum)
x_sumsqr <- calc(x_based_on_mag, fx.sumsqrs)
# y_var
y_based_on_mag <- r6
y_sum <- calc(y_based_on_mag, fx.sum)
y_sumsqr <- calc(y_based_on_mag, fx.sumsqrs)
# Metrics
fmean = (sqrt((x_sum/fvalid)^2 + (y_sum/fvalid)^2))
fvar = (x_sumsqr + y_sumsqr)/fvalid
fsd = sqrt(fvar)
fcv = fsd/fmean
fprob = fvalid/fclear_m
fintst = fmean * fprob
fpers <- overlay(fsd, fun=rc)
fpersprob = fpers * fprob
```

Plotting metrics using static threshold

```{r}

pdf(file = 'metrics_static_front_wk_20_2021.pdf', width = 10, height = 6)
par(mfrow = c(2,4), oma = c(1,1,1,1))
plot(fvalid, main = 'Fvalid', col= pal)
plot(fclear_m, main = 'Fclear', col= pal)
plot(fmean, main = 'Frontal Mean', col= pal)
plot(fprob, main = 'Frontal Probability', col= pal)
plot(fvar, main = 'Frontal Variance', col= pal)
plot(fsd, main = 'Frontal Standard Deviation', col= pal)
plot(fcv, main = 'Frontal CV', col= pal)
plot(fintst, main = 'Frontal Intensity', col= pal)
plot(fpers, main = 'Frontal Persistence', col= pal)
plot(fpersprob, main = 'Persistence Probability', col = pal)
dev.off()


```


#### Self detecting threshold for frontal detection using moving average

Trying this with terra package: 

```{r}
# Metrics 
# Select a single layer (week) to test metric calculations
# sgspr <- r.grad.mur[[21]]
# sfspr <- r.front.m[[21]]
# sxspr <- r.xcomp.m[[21]]
# syspr <- r.ycomp.m[[21]]

# -- stack, note this is different for terra:spatrasters -- # 
sgspr <- terra::rast(sr.grad.m[1:7]) # this only gets 2 layers
sfspr <- terra::rast(sr.focal.front.m[1:7])
sxspr <- terra::rast(sr.xcomp.m[1:7])
syspr <- terra::rast(sr.ycomp.m[1:7])

sgspr <- grad.stack.f
sfspr <- front.stack.f
sxspr <- x.stack.f
syspr <- y.stack.f


# Set threshold for low temporal variability 
range(na.omit(sfspr))
pers_thresh <- 0.08
## Initialize these
r1 = sxspr # stack of x
r3 = sfspr # stack of fronts
# r3[r3 <= 0] <- NA # do I need to do this? 
plot(r3, col = pal,  main = 'fronts NA')
#plot(sfspr, col = pal,  main = 'Fronts')
# r4 <- terra::mask(r1, r3)
# r4.t <- terra::mask(r3, r1)
# plot(r4, col = pal, main = 'x based on grad mag') # selects values of x only if pixel indicated as frontal from grad_mag

# rcx1 <- classify(r1, r3)
# test = terra::extract(r1[[1]], r3[[1]], exact=TRUE)
# test = terra::extract(r1, r3, exact=TRUE)
# s3 <- ifel(is.na(r1), NA, r3)

#   r.f[r.f <= tmp.foc] <- 0
# This is how I determined a front, if pixel in frontal raster was less than 
# or equal to tmp.foc, it received a zero (tmp.foc is the focal window)
r.f[r.f <= tmp.foc] <- 0
# Next, I used an ifelse statement to create a new spat raster where 
# if a pixel in the stack of fronts == 0, then it was assigned an NA 
# otherwise it received the coincident value from stack of x's
foc.alt <- ifel(r3==0, NA, r3) # setting non-frontal values to NA 
test.2 <- ifel(r3==0, NA, r1) # setting non-frontal values to 0 .. see notes 
# about which is better to do
plot(test.2, col = pal)
plot(r3, col = pal,  main = 'fronts NA')
# remove from r1(stack of x) all values that are NA in r3(stack of fronts)
test.2.mask <- terra::mask(r1, foc.alt)
# compare the two approaches, may be easier to assign NA to r.f upstream
plot(test.2[[3]])
plot(test.2.mask[[3]])
# mask removes all values from one layer that are NA in another layer, 
# cover combines two layers by taking the values of the first layer except where 
# these are NA
# They are the same, so just do the test.2 approach its more straightforward for 
# now
r4 <- ifel(r3==0, NA, r1) # x-based on frontal pixels 

# plot(r4, col = pal, main = 'x based on grad mag')
# plot(r3, col = pal, main = 'fronts')
r5 = syspr # stack of y
r6 <- ifel(r3==0, NA, r5) # y-based on frontal pixels 
#plot(r6, col = pal, main = 'y based on grad mag')
## Base params
fvalid <- terra::app(sfspr, fx.sum.greater.than.zero)# calc with raster package
m_sum <- terra::app(sfspr, fx.sum)
fclear_m <- terra::app(sgspr, fx.sum.greater.than.zero)
# x_var
x_based_on_mag <- r4
x_sum <- terra::app(x_based_on_mag, fx.sum)
x_sumsqr <- terra::app(x_based_on_mag, fx.sumsqrs)
# y_var
y_based_on_mag <- r6
y_sum <- terra::app(y_based_on_mag, fx.sum)
y_sumsqr <- terra::app(y_based_on_mag, fx.sumsqrs)
# Metrics
fmean = (sqrt((x_sum/fvalid)^2 + (y_sum/fvalid)^2))
fvar = (x_sumsqr + y_sumsqr)/fvalid
fsd = sqrt(fvar)
fcv = fsd/fmean
fprob = fvalid/fclear_m
fintst = fmean * fprob
fpers <- terra::ifel(fsd <= pers_thresh, 1, 0)
fpersprob = fpers * fprob



```


Plotting metrics using focal weighted threshold

```{r}

pdf(file = 'metrics_focal_front_wk_20_2021.pdf', width = 10, height = 6)
par(mfrow = c(2,4), oma = c(1,1,1,1))
plot(fvalid, main = 'Fvalid', col= pal)
plot(fclear_m, main = 'Fclear', col= pal)
plot(fmean, main = 'Frontal Mean', col= pal)
plot(fprob, main = 'Frontal Probability', col= pal)
plot(fvar, main = 'Frontal Variance', col= pal)
plot(fsd, main = 'Frontal Standard Deviation', col= pal)
plot(fcv, main = 'Frontal CV', col= pal)
plot(fintst, main = 'Frontal Intensity', col= pal)
plot(fpers, main = 'Frontal Persistence', col= pal)
plot(fpersprob, main = 'Persistence Probability', col = pal)
dev.off()


```

Trying this with raster package: 


```{r}

## Modis
ra.grad.m <- list()
ra.xcomp.m <- list()
ra.ycomp.m <- list()
ra.front.m <- list()
#threshold = 0.18 # this is for static threshold method, not focal method
# for (i in 1:52){ will need when fixed
for (i in 1:7){
  tmp.g <- (grad.m[,,i]) 
  tmp.gt <- t(tmp.g) 
  r.g = raster(tmp.gt, xmn = min(lon), xmx = max(lon), 
               ymn = min(lat), ymx = max(lat),
               crs = CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs+ towgs84=0,0,0"))
  r.g = raster::flip(r.g,2)  
  #plot(r.g, col = pal)
  assign(paste('r.g.',i, sep = ''), r.g)
  ra.grad.m[[i]] <- get(paste0('r.g.',i))
  tmp.x <- (x.m[,,i]) 
  tmp.xt <- t(tmp.x)
  r.x = raster(tmp.xt, xmn = min(lon), xmx = max(lon), 
               ymn = min(lat), ymx = max(lat),
               crs = CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs+ towgs84=0,0,0"))
  r.x = raster::flip(r.x,2)  
  assign(paste('r.x.',i, sep = ''), r.x)
  ra.xcomp.m[[i]] <- get(paste0('r.x.',i))
  tmp.y <- (y.m[,,i]) 
  tmp.yt <- t(tmp.y)
  r.y = raster(tmp.yt, xmn = min(lon), xmx = max(lon), 
               ymn = min(lat), ymx = max(lat),
               crs = CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs+ towgs84=0,0,0"))
  r.y = raster::flip(r.y,2)  
  assign(paste('r.y.',i, sep = ''), r.y)
  ra.ycomp.m[[i]] <- get(paste0('r.y.',i))
  # Change this to reflect new front detection method
  # tmp.f <- (grad.m[,,i])
  # tmp.f[tmp.f < threshold] <- 0
  # tmp.ft <- t(tmp.f)
  # r.f = raster(tmp.ft, xmn = min(lon), xmx = max(lon),
  #              ymn = min(lat), ymx = max(lat),
  #              crs = CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs+ towgs84=0,0,0"))
  # r.f = raster::flip(r.f,2)
  # plot(r.f, col = pal)
  # assign(paste('r.f.',i, sep = ''), r.f)
  # ra.front.m[[i]] <- get(paste0('r.f.',i))
}


ra.front.m <- list()
for (i in 1:7){
 # This reflects new front detection method
  tmp.f <- (grad.m[,,i])
  tmp.ft <- t(tmp.f)
  r.f = raster(tmp.ft, xmn = min(lon), xmx = max(lon),
               ymn = min(lat), ymx = max(lat),
               crs = CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs+ towgs84=0,0,0"))
  #r.f.bt = raster::flip(r.f,2)
  r.f = raster::flip(r.f,2)
  plot(r.f)
  #plot(r.f.bt, col = pal)
  r.f.og <- r.f
  tmp.foc <- raster::focal(r.f, fun=mean, 
                           na.rm=TRUE,    w=matrix(1/9,nrow=3,ncol=3))
  
  r.f[r.f >= tmp.foc] <- r.f
  id_raster_sub <- id_raster[[1]]>2
  catch_raster_sub <- mask(catch_raster,id_raster_sub/id_raster_sub)

  assign(paste('r.f.',i, sep = ''), r.f)
  ra.front.m[[i]] <- get(paste0('r.f.',i))
  
}

front.stack.f.rasterpackage <- stack(ra.front.m)
  r.f.t <- ifelse(r.f <= tmp.foc, 0,r.f)
  r.f.t <- r.f <= tmp.foc
# remove from r1(stack of x) all values that are NA in r3(stack of fronts)
r.f.mask <- raster::mask(r.f,tmp.foc)
foc.df <- as.data.frame(tmp.foc, xy = TRUE) # this works with Raster* objects as well
foc.df$layer[is.nan(foc.df$layer)]<-NA
front.df <- as.data.frame(r.f, xy = TRUE) # this works with Raster* objects as well
locs.rm.front <- which(na.omit(front.df$layer) >= na.omit(foc.df$layer))
front.df.foc <- front.df[locs.rm.front,]
rrr = rasterFromXYZ(front.df.foc)  
r.f.subs <- subs(r.f,foc.df)


```

visualizing to see if the method worked

```{r}

plot(tmp.foc, main = 'focal')
plot(r.f.bt, main = 'fronts before thresh')
plot(r.f, main = 'fronts after thresh')
#plot(r.f.t, main = 'fronts after thresh v2')
plot(r.f.mask, main = 'r.f.mask')
plot(rrr, main = 'after')
```





There is an issue with fvalid - it looks the same as fclear, that is likely bc
the frontal threshold based on focal window did not work ? 


```{r}
# Metrics

# -- stack -- # 
sfspr <- front.stack.f.rasterpackage

# Set threshold for low temporal variability 
range(na.omit(sfspr))
range(na.omit(sgspr@data@values))
pers_thresh <- 0.08
## Initialize these
r1 = sxspr # stack of x
r3 = sfspr # stack of fronts
r3[r3 <= 0] <- NA # do I need to do this? - yes for mask*
plot(r3, col = pal,  main = 'fronts NA')
# remove from r1(stack of x) all values that are NA in r3(stack of fronts)
r4 <- raster::mask(r1, r3)
plot(r4, col = pal, main = 'x based on grad mag')
r5 = syspr # stack of y
r6 <- raster::mask(r5, r3)
plot(r6, col = pal, main = 'y based on grad mag')
## Base params
fvalid <- calc(sfspr, fx.sum.greater.than.zero)
m_sum <- calc(sfspr, fx.sum)
fclear_m <- calc(sgspr, fx.sum.greater.than.zero)
# x_var
x_based_on_mag <- r4
x_sum <- calc(x_based_on_mag, fx.sum)
x_sumsqr <- calc(x_based_on_mag, fx.sumsqrs)
# y_var
y_based_on_mag <- r6
y_sum <- calc(y_based_on_mag, fx.sum)
y_sumsqr <- calc(y_based_on_mag, fx.sumsqrs)
# Metrics
fmean = (sqrt((x_sum/fvalid)^2 + (y_sum/fvalid)^2))
fvar = (x_sumsqr + y_sumsqr)/fvalid
fsd = sqrt(fvar)
fcv = fsd/fmean
fprob = fvalid/fclear_m
fintst = fmean * fprob
fpers <- overlay(fsd, fun=rc)
fpersprob = fpers * fprob
```

Plotting metrics using focal threshold with raster package instead of terra

```{r}

pdf(file = 'metrics_focal_front_wk_20_2021_raster_package.pdf',
    width = 10, height = 6)
par(mfrow = c(2,4), oma = c(1,1,1,1))
plot(fvalid, main = 'Fvalid', col= pal)
plot(fclear_m, main = 'Fclear', col= pal)
plot(fmean, main = 'Frontal Mean', col= pal)
plot(fprob, main = 'Frontal Probability', col= pal)
plot(fvar, main = 'Frontal Variance', col= pal)
plot(fsd, main = 'Frontal Standard Deviation', col= pal)
plot(fcv, main = 'Frontal CV', col= pal)
plot(fintst, main = 'Frontal Intensity', col= pal)
plot(fpers, main = 'Frontal Persistence', col= pal)
plot(fpersprob, main = 'Persistence Probability', col = pal)
dev.off()


```






### MUR
*Note: there is a problem with the f_clear. MUR is interpolated, so there are
no cloud days, therefore f_clear is always 100 and messes up the metrics. 
***NOTE 2: That doesnt make sense- find error

```{r}
# substitute a single layer (week) to test metric calcs
sgspr <- r.grad.mur[[21]]
sfspr <- r.front.mur[[21]]
sxspr <- r.xcomp.mur[[21]]
syspr <- r.ycomp.mur[[21]]
# Metrics
## Initialize these
r1 = sxspr # stack of x
r3 = sfspr # stack of fronts
r3[r3 <= 0] <- NA # do I need to do this? 
plot(r.g.21, col = pal, main = 'gradient magnitude')
plot(r.f.21, col = pal, main = 'fronts (no NA)') # plot the fronts 
plot(r3, col = pal,  main = 'fronts NA')
r4 <- raster::mask(r1, r3)
plot(r4, col = pal, main = 'x based on grad mag')
r5 = syspr # stack of y
r6 <- raster::mask(r5, r3)
plot(r6, col = pal, main = 'y based on grad mag')
## Base params
fvalid <- calc(sfspr, fx.sum.greater.than.zero)
m_sum <- calc(sfspr, fx.sum)
fclear_m <- calc(sgspr, fx.sum.greater.than.zero)
# x_var
x_based_on_mag <- r4
x_sum <- calc(x_based_on_mag, fx.sum)
x_sumsqr <- calc(x_based_on_mag, fx.sumsqrs)
# y_var
y_based_on_mag <- r6
y_sum <- calc(y_based_on_mag, fx.sum)
y_sumsqr <- calc(y_based_on_mag, fx.sumsqrs)
# Metrics
fmean = (sqrt((x_sum/fvalid)^2 + (y_sum/fvalid)^2))
fvar = (x_sumsqr + y_sumsqr)/fvalid
fsd = sqrt(fvar)
fcv = fsd/fmean
fprob = fvalid/fclear_m
fintst = fmean * fprob
fpers <- overlay(fsd, fun=rc)
fpersprob = fpers * fprob

```

Quick visual 

```{r}
# just checking ...
plot(fclear_m, main = 'Fclear', col= pal)
plot(fvalid, main = 'fvalid', col= pal)
par(mfrow=c(1,3))
plot(sgspr[[1]], main = 'grad_mag month 1', col= pal)
plot(sgspr[[2]], main = 'grad_mag month 2', col= pal)
plot(sgspr[[3]], main = 'grad_mag month 3', col= pal)

range(na.omit(sgspr[[1]]@data@values))
range(na.omit(sgspr[[2]]@data@values))
range(na.omit(sgspr[[3]]@data@values))

pdf(file = 'metrics_spring_1990_4km_thresh12.pdf', width = 10, height = 6)
par(mfrow = c(2,4), oma = c(1,1,1,1))
plot(fvalid, main = 'fvalid', col= pal)
plot(fclear_m, main = 'Fclear', col= pal)
plot(fmean, main = 'Frontal Mean', col= pal)
plot(fprob, main = 'Frontal Probability', col= pal)
plot(fvar, main = 'Frontal Variance', col= pal)
plot(fsd, main = 'Frontal Standard Deviation', col= pal)
plot(fcv, main = 'Frontal CV', col= pal)
plot(fintst, main = 'Frontal Intensity', col= pal)
plot(fpers, main = 'Frontal Persistence', col= pal)
plot(fpersprob, main = 'Persistence Probability', col = pal)
dev.off()

```















